---
title: "Logistic Regression Predict Fish Weight"
author: "Eduardo Noriega"
date: "November 16,2022"
output: html_document
---
 

```{r include=FALSE,echo=FALSE}
require(tigerstats)
require(tidyverse)
library (leaps)
```

## import fist CSV using the import function that Luz found

# Predicting Fish Weight  

```{r}
Fish = read.csv('Fish.csv')
Perch = filter(Fish, Species == 'Perch')
Perch = subset (Perch, select= -Species)
weightPerch = lm(Weight~Length1+Length2+Length3+Height+Width,data=Perch)
summary.lm(weightPerch)
```




## Perch

### Best Models

### Best Two regressor model
```{r}
regsubsets.out <-
    regsubsets(Weight ~. , data = Perch,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
```
The Best two variables are height and width.




## Pike

```{r}
Fish = read.csv('Fish.csv')
Pike = filter(Fish, Species == 'Pike')
Pike = subset (Pike, select= -Species)
weightPike = lm(Weight~Length1+Length2+Length3+Height+Width,data=Pike)
summary.lm(weightPike)
```

```{r}
regsubsets.out <-
    regsubsets(Weight ~. , data = Pike,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
```

Length1 and Length3 are the best two models.




### Best Models


## Roach
```{r}
Fish = read.csv('Fish.csv')
Roach = filter(Fish, Species == 'Roach')
Roach = subset (Roach, select= -Species)
weightRoach = lm(Weight~Length1+Length2+Length3+Height+Width,data=Roach)
summary.lm(weightRoach)
```



### Best Two regressor model
```{r}
regsubsets.out <-
    regsubsets(Weight ~. , data =Roach,
               nbest = 1,       # 1 best model for each number of predictors
               nvmax = NULL,    # NULL for no limit on number of variables
               force.in = NULL, force.out = NULL,
               method = "exhaustive")

summary.out <- summary(regsubsets.out)
as.data.frame(summary.out$outmat)
```

The best two models are Width and Length3


### Best Models

### Best Two regressor model

## Final Summary Statements
The adjusted R-squared=0.9372 for Perch, adjusted R-squared=0.9794 for Pike,and the adjusted R-squared=0.821 for Roach. Pike has the highest adjusted r-squared where it Length1 and Length3 were the best models for it.
